%\section{}
%\pagestyle{plain}   %Use if you do not want the fancy headers and footers... 
					 %({plain} -> just page number, {empty} -> nothing)...
					 % this will change all pages that come after this tex file...
					 % so make sure to reset the pagestyle to {fancy} at the end of this file
Outline:
SAFT\newline
liquid-vapor+run-absolute\newline
How comparisons were made\newline
\section{Partition function seperation}
The Monte Carlo simulations can be partitioned into high and low temperature regimes. At low temperature the interactions dominate, while at high temperatures the entropy dominates. Both regimes can be partitioned yet again by seperating the kinetic energies into an ideal gas term. In terms of equations, we start with the partition function and seperate the summation into the three partitions:
$$\newline Z=\frac{1}{N!}\sum_i e^{-\beta\cdot E_i}
\newline Z=\frac{1}{N!}\int\cdot\cdot\cdot\int e^{-\beta\cdot [\{P_{1}^2/{2m}+P_{2}^2/{2m}+...\}+V(\vec{R_1},\vec{R_2},...)]}d\vec{P_1}\cdot d\vec{P_2}\cdot\cdot\cdot d\vec{P_N}\cdot d\vec{R_1}\cdot d\vec{R_2}\cdot\cdot\cdot d\vec{R_N}\newline$$
The momentum integrals are independent of the position integrals, so we seperate the momentum integrals which we then incorporate into an ideal gas term by multiplying by $V^N/V^N$.
$$\newline Z=\boldsymbol{Z_{ideal} \cdot \frac{1}{V^N}}\cdot \int\cdot\cdot\cdot\int e^{-\beta\cdot V(\vec{R_1},\vec{R_2},...)}d\vec{R_1}\cdot d\vec{R_2}\cdot\cdot\cdot d\vec{R_N}\newline$$
where $$Z_{ideal}=V^N\cdot\frac{1}{N!}\int\cdot\cdot\cdot\int e^{-\beta\cdot [P_{1}^2/{2m}+P_{2}^2/{2m}+...]}d\vec{P_1}\cdot d\vec{P_2}\cdot\cdot\cdot d\vec{P_N}\newline$$
The remaining potential energy term is seperated into the low temperature and high temperature regime. At high temperatures, the atom energies are much higher than the potential well; this means the finite potential well can be considered zero. However; even at infinite temperature the atoms are assumed to be a hard sphere. This hard sphere behavior is incorporated into the partition function by multiplying by $Z_{HS}/Z_{HS}$.
$\newline Z=Z_{ideal}\cdot \boldsymbol{Z_{HS}\cdot \frac{1}{Z_{HS}}}\cdot \frac{1}{V^N}\cdot \int\cdot\cdot\cdot\int e^{-\beta\cdot V(\vec{R_1},\vec{R_2},...)}d\vec{R_1}\cdot d\vec{R_2}\cdot\cdot\cdot d\vec{R_N}\newline$
where $Z_{HS}=\frac{1}{V^N}\int\cdot\cdot\cdot\int e^{-\beta\cdot V_{HS}(\vec{R_1},\vec{R_2},...)}d\vec{R_1}\cdot d\vec{R_2}\cdot\cdot\cdot d\vec{R_N}\newline$
The last part is just the ratio between the interaction and the hard sphere partition function; we call this the dispersive term.
$\newline Z=Z_{ideal}\cdot Z_{HS}\cdot \boldsymbol{\frac{Z_{interaction}}{Z_{HS}}}=Z_{ideal}\cdot Z_{HS}\cdot \boldsymbol{Z_{disp}}\newline$
where $Z_{interaction}=\frac{1}{V^N}\cdot \int\cdot\cdot\cdot\int e^{-\beta\cdot V(\vec{R_1},\vec{R_2},...)}d\vec{R_1}\cdot d\vec{R_2}\cdot\cdot\cdot d\vec{R_N}\newline$
and $Z_{disp}= \frac{Z_{interaction}}{Z_{HS}}\newline$

\section{Free Energy via Monte Carlo Simulations}
Given the separated partition function, the free energies are just the sum of the free energies due to the ideal term, the hard sphere term, and the dispersive term. The ideal term is ignored because it stays the same between theory and the Monte Carlo simulations. Due to the finite nature of the Monte Carlo simulations, the hard sphere term in the simulations aren't exactly the hard sphere terms in theory. Although we can make some corrections due to the finite nature, ultimately we have to enforce the boundary condition that at high temperature the atoms behave like hard spheres. Given this boundary condition, we are then able to define what the dispersion term should be based on estimation of the density of states.
\subsection{ideal gas free energy}
To find the ideal gas free energy we can use previous results based on knowing the entropy of the system which we can then use to find $F_{ideal}=U_{ideal}-T\cdot S_{ideal}$.
$$U_{ideal}=3/2\cdot N\cdot k\cdot T$$
$$S_{ideal^*}\approx k\cdot N \left ( ln\left [ \frac{V}{N}\left ( \frac{4\cdot \pi\cdot m}{3\cdot h^2}\cdot \frac{U}{N} \right)^{3/2} \right]+\frac{5}{2}\right )$$

The Sackur-Tetrode equation with the Stirling approximation actually does not make physical sense as the entropy per particle at constant temperature only depends on density. A simple example can show why this doesn't make sense. Consider two atoms in boxes seperated by a partition, and compare the entropy per particle to when the partition in the box has been removed. Once the partition has been removed, the two atoms can explore many more configurations than previously, which means the entropy should have increased once the two atoms were allowed to mix. Unfortunately the Sackur-Tetrode equation with Stirlings approximation would predict the entropy per particle with or without the partition should be the same. This is a bit of a problem since every box in a Monte Carlo simulation will contain exactly N particles, which means the entropy is actually lower than a real ideal gas.

The entropy problem can be fixed by using the Sackur-Tetrode equation without Stirling's approximation. Essentially use a constant density and compare the entropy per particle of a small box to the entropy per particle of a large box. The difference in entropy shows how the ideal gas entropy within a box will deviate from the expected ideal gas entropy.

$$S_{ideal}=k\cdot N \left ( ln\left [ V\cdot N!^{-1/N}\left ( \frac{4\cdot \pi\cdot m}{3\cdot h^2}\cdot\frac{U}{N} \right)^{3/2}  \right]+\frac{3}{2}\right )$$

It would be natural to think we can just incorporate this deviation in entropy for the Monte Carlo simulations, unfortunately the simulations contain an intractable problem involving the periodic nature of the simulations. The atoms in the box are repeated in a periodic way to represent the atoms in the entire fluid, however by forcing a periodic boundary condition the entire state of a fluid is now defined by only the atoms within the small box. It is very unlikely that 100 atoms can fully define a system containing an Advogadro's number of atoms, so the entropy should be much less than a realistic system. Rather than incorporate such a change in entropy, we instead must recognize that these Monte Carlo simulations are defining the boundary conditions relative to the smaller sub system; this is basically the equivalent of mean field theory where the boundary is defined by the smaller sub system. 

Recognizing that Monte Carlo simulations are a variation of mean field theory, the loss in entropy due to reduced configurations is ignored. Instead the boundary conditions are enforced. At any temperature we expect the kinetic energies to behave like an ideal gas. At high temperatures we expect the system to behave like a hard sphere system.

\subsection{hard sphere free energy}
The hard sphere partition function can be found by calculating the excess entropy at $T\to\infty$. This can be seen as follows:
$$Z_{exc}=Z_{HS}\cdot Z_{disp}\Rightarrow$$
$$\newline F_{exc}=-k\cdot T\cdot ln(Z_{exc})=-k\cdot T\cdot ln(Z_{HS})-k\cdot T\cdot ln(Z_{disp})\Rightarrow $$
$$\newline S_{exc.\infty}=\lim_{T\to\infty}-\left ( \frac{\partial F_{exc}}{\partial T} \right ) _{V,N} \text{ but }\lim_{T\to\infty}Z_{exc}=\text{constant}\Rightarrow$$
$$\newline S_{exc.\infty}=-k\cdot ln(Z_{HS.\infty})-k\cdot ln(Z_{disp.\infty})$$
$$\newline \text{but }Z_{HS}\text{ is constant and }Z_{disp.\infty}=Z_{interaction.\infty}/Z_{HS}=Z_{HS}/Z_{HS}=1 \Rightarrow$$
$$S_{exc.\infty}=-k\cdot ln(Z_{HS})-k\cdot ln(1)=-k\cdot ln(Z_{HS}) \Rightarrow$$
$$\newline Z_{HS}=e^{-S_{exc.\infty}/k}$$

To find the hard sphere partition function, we need to find the maximum excess entropy as $T\to\infty$. The method used to find the maximum excess entroy starts by considering N atoms in an extremely large box. The hard sphere component in 
\subsection{dispersive free energy}
The dispersive term is found by estimating the density of states using a * method. The main problem is the density of states is found by sampling the energy levels, but the relative distribution of energy levels is not unique to a single density of states. In other words, the partition function can be changed by an arbitrary factor without actually changing the total energy. This can be seen as follows:

Suppose $$Z=\sum_i D(E_i)\cdot e^{-\beta\cdot E_i}$$

then $$U=\sum_i E_i\cdot D(E_i)\cdot e^{-\beta\cdot E_i}/Z\newline$$

Now suppose we let $$D_2(E_i)=\alpha\cdot D(E_i)$$

then $$Z_2=\sum_i \alpha\cdot D(E_i)\cdot e^{-\beta\cdot E_i}=\alpha\cdot Z\Rightarrow\newline$$
$$U_2=\sum_i E_i\cdot D_2(E_i)\cdot e^{-\beta\cdot E_i}/Z_2$$
$$\newline U_2=\sum_i E_i\cdot \boldsymbol{\alpha}\cdot D(E_i)\cdot e^{-\beta\cdot E_i}/(\boldsymbol{\alpha}\cdot Z)$$
$$\newline U_2=\sum_i E_i\cdot D(E_i)\cdot e^{-\beta\cdot E_i}/Z$$
$$\newline U_2=U\newline$$
Basically the partition function will define the total energy at all temperatures, but knowing the total energy at all temperatures will not define a unique partition function. Specifically, the partition function up to some arbitrary factor will give the same total energy. This is a bit problematic considering the method to find the density of states makes observations of the total energy to estimate the density of states, which then results in a density of states that is only defined up to some unknown factor.

To get around this problem of an unknown factor in the density of states, note that the dispersive partition function will go towards one as T approaches infinity. This happens because $Z_{disp}$ is the ratio of the interaction term to the hard sphere term, and the interaction term approaches the hard sphere term as the temperature increases. Essentially we can leave the unkown $\alpha$ term alone, and it will show up in both the interaction and hard sphere partition function.

That is: $$Z_{disp}=\frac{Z_{interaction}}{Z_{HS}}=\frac{\sum_i \alpha\cdot D(E_i)\cdot e^{-beta\cdot E_i}}{\lim_{T\to\infty}\sum_i \alpha\cdot D(E_i)\cdot e^{-\beta\cdot E_i}}=\frac{\sum_i D(E_i)\cdot e^{-\beta\cdot E_i}}{\sum_i D(E_i)}$$

\section{SAFT}
SW.fid+SW.fdisp+SW.fhs Explain.

\subsection{$S_{exc.\infty}$}



%\pagestyle{fancy}   % Reset all pages after this file to fnacy headers